A quantitative framework for investigating the reliability of network construction: supplemental information

### 2018-03-21 manuscript/supplemental.tex
removed comments from main text prior to upload

      \vspace{12pt}
      \begin{em}
      \noindent \hspace{2pt}\# Now get the degree distributions from the web\\
      \noindent \hspace{2pt}deg\_dist\_Salix=rowSums(prior\_web)/ncol(prior\_web)\\
      \vspace{4pt}
      \noindent \hspace{2pt}\# Remove one genotype that never interacted\\
      \noindent \hspace{2pt}deg\_dist\_Salix\textless-deg\_dist\_Salix[which(rowSums(prior\_web)\textgreater0)]\\
      \noindent \hspace{2pt}deg\_dist\_galler=colSums(prior\_web)/nrow(prior\_web)\\
      \vspace{4pt}
      \noindent \hspace{2pt}\# Interaction probabilities are the product of plant and galler probabilities\\
      \noindent \hspace{2pt}int\_probs=as.numeric(deg\_dist\_galler\%$*$\%t(deg\_dist\_Salix))\\
      \vspace{4pt}
      \noindent \hspace{2pt}\# And for the galler-parasitoid web:\\
      \noindent \hspace{2pt}deg\_dist\_parasitoid=rowSums(prior\_web\_para\_only)/ncol(prior\_web\_para\_only)\\
      \noindent \hspace{2pt}deg\_dist\_parasitized=colSums(prior\_web\_para\_only)/nrow(prior\_web\_para\_only)\\
      \noindent \hspace{2pt}gp\_int\_probs=as.numeric(deg\_dist\_parasitized\%$*$\%t(deg\_dist\_parasitoid))\\
      \end{em}

@@

      % deg_dist_parasitoid=rowSums(GP_web)/ncol(GP_web)
      % deg_dist_parasitized=colSums(GP_web)/nrow(GP_web)
      % gp_int_probs=as.numeric(deg_dist_parasitized%*%t(deg_dist_parasitoid))

>>>>

      \vspace{12pt}
      \begin{em}
      \noindent \hspace{2pt}\# Now get the degree distributions from the web\\
      \noindent \hspace{2pt}deg\_dist\_Salix=rowSums(prior\_web)/ncol(prior\_web)\\
      \vspace{4pt}
      \noindent \hspace{2pt}\# Remove one genotype that never interacted\\
      \noindent \hspace{2pt}deg\_dist\_Salix\textless-deg\_dist\_Salix[which(rowSums(prior\_web)\textgreater0)]\\
      \noindent \hspace{2pt}deg\_dist\_galler=colSums(prior\_web)/nrow(prior\_web)\\
      \vspace{4pt}
      \noindent \hspace{2pt}\# Interaction probabilities are the product of plant and galler probabilities\\
      \noindent \hspace{2pt}int\_probs=as.numeric(deg\_dist\_galler\%$*$\%t(deg\_dist\_Salix))\\
      \vspace{4pt}
      \noindent \hspace{2pt}\# And for the galler-parasitoid web:\\
      \noindent \hspace{2pt}deg\_dist\_parasitoid=rowSums(prior\_web\_para\_only)/ncol(prior\_web\_para\_only)\\
      \noindent \hspace{2pt}deg\_dist\_parasitised=colSums(prior\_web\_para\_only)/nrow(prior\_web\_para\_only)\\
      \noindent \hspace{2pt}gp\_int\_probs=as.numeric(deg\_dist\_parasitised\%$*$\%t(deg\_dist\_parasitoid))\\
      \end{em}

@@

      % deg_dist_parasitoid=rowSums(GP_web)/ncol(GP_web)
      % deg_dist_parasitised=colSums(GP_web)/nrow(GP_web)
      % gp_int_probs=as.numeric(deg_dist_parasitised%*%t(deg_dist_parasitoid))
